The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-14 Fsing/TestIdealsPaper/TestIdeals.tex
Changes in doc for testModule

The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{isCohenMacaulay} is set to \texttt{true}. If the ring
is not Cohen-Macaulay then \texttt{false} is returned. Next, the algorithm
computes the test module $M \subseteq \omega_{R}$ and checks to see if
$\omega_{R} \subseteq M$;  see the next section for the description of a test module.

>>>>

The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{AssumeCM} is set to \texttt{true}. If the ring
is not Cohen-Macaulay then \texttt{false} is returned. Next, the algorithm
computes the test module $M \subseteq \omega_{R}$ and checks to see if
$\omega_{R} \subseteq M$;  see the next section for the description of a test module.
